---
title: "MATH 341 - Homework 04"
author: "Marjorie Blanco"
date: "January 29, 2018"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 5.5 Coffee

## Population

The population is all the coffee manufacture by company.

## Confidence Interval at 95%

```{r}
sd.coffee <- 7.1       #mg
N <- 50                #units
mean.coffee <- 110     #mg

z <- qnorm(.025, lower.tail = FALSE)
z

error <- qnorm(.025, lower.tail = FALSE) * sd.coffee / sqrt(N)
lower <- mean.coffee - error
upper <- mean.coffee + error

error
lower
upper
```

The lower limit is `r round(lower,2)`.

The upper limit is `r round(upper,2)`.

If the sampling and estimation procedure is repeated many time, the confidence interval would include the population mean 95% of the time.

## Interpretation

We are 95% confident that the average caffeine content is between `r round(lower,2)` and `r round(upper,2)` milligrams.

# Problem 5.8 Mean Net Profit Margin

## Confidence Interval at 99%

```{r}
mean.netprofitmargin <- 0.072       
N <- 15                           
sd.netprofitmargin <- 0.125     

error <- qnorm(.005, lower.tail = FALSE) * sd.netprofitmargin / sqrt(N)

error <- qt(0.995,df=N-1)*  sd.netprofitmargin/sqrt(N)
lower <- mean.netprofitmargin - error
upper <- mean.netprofitmargin + error

error
lower
upper
```

## Interpretation

We are 99% confident that the mean gross profit margin of all small business in the city is between `r round(lower*100,2)` % and `r round(upper*100,2)` %

# Problem 5.13  Antibiotics

```{r}
sd.bacteria <- 13       #cm^2
e.bacteria <- 3         #cm^2
a <- 0.01

N <-  qnorm(a/2)^2 * sd.bacteria^2 / e.bacteria^2
N
```

The number of observations (cultures that must be developed and then tested) is `r round(N,0)`.

# Problem 10.7 False Positive

```{r}
N <- 10000
p <- 591 / N
q <- 1 - p
p
q


error <- qnorm(.005, lower.tail = FALSE) *  sqrt((p*q)/N)
lower <- p - error
upper <- p + error

error
lower
upper

```

## Interpretation

We are 99% confident that the interval `r round(lower,2)` and `r round(upper,2)` contains the true proportion of false positives.
